---
title: "Shiny App for Air Pollution in Delhi"
author: "Adeel"
date: "11/08/2020"
output: slidy_presentation
---

## What is Shiny?

- Shiny is an open source R package to make powerful webapps.
- You can host free apps through Shiny servers. 
- Best part you don't need HTML, CSS or Java script. 


## What about this Shiny App all about?

- The idea is to show a spatial temporal variation of air quality in Delhi
- For this I took 2019 air quality data of Delhi from 30 stations in Delhi. 
- Then create a spatial maps using IDW (Inverse Distance Weighting) method. 
- In this app I try to utilize leaflet and various packages that I learned from Data Science Course. 

## This is how a leaflet map for January month looks like 
```{r,include=FALSE}
library(sf)
library(sp)
library(gstat)
library(rgdal)
library(RColorBrewer)
library(raster)
library(mapview)
library(leaflet)
```

```{r,include=FALSE}
PM25 <- read.csv("data/PM25_Month.csv",col.names = c("Number","Station_Name","Location","Latitude","Longitude",                                                     "January","February","March","April","May","June","July","August","September","October","November","December"))
coordinates(PM25) <- ~Longitude + Latitude  
proj4string(PM25)=CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0")
# Changing the Projection
PM25_T <- spTransform(PM25, CRS("+proj=utm +zone=43 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"))

# Reading the Shape file of Munich
Delhi <- readOGR("data/Shape file/delhi.shp")
Delhi_T <- spTransform(Delhi, CRS("+proj=utm +zone=43 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")) 

# Crating Grids for Munich
grdpts <- makegrid(Delhi_T)
spgrd <- SpatialPoints(grdpts, proj4string = CRS(proj4string(Delhi_T)))
spgrdWithin <- SpatialPixels(spgrd[Delhi_T,])
plot(spgrdWithin)

```

```{r,include=FALSE}
PM25.idw_Jan <- gstat::idw(January ~ 1, PM25_T, newdata=spgrdWithin, idp=2.0)
raster_IDW  <- raster(PM25.idw_Jan)
red_colors <- brewer.pal(9, "Reds") %>%
            colorRampPalette()

```

```{r,echo=FALSE,warning=FALSE}
mapview(raster_IDW,alpha=0.4,na.color="transparent",col.regions=red_colors,legend.pos="bottomright",layer.name="PM2.5") + mapview(PM25_T, zcol = "Station_Name",legend=FALSE)
```

## With Shiny I added a time slider that can integrate different months too

### You can check out the app and also source code through :
- Deployed at [https://adeel707.shinyapps.io/Air_Quality_Delhi/](https://adeel707.shinyapps.io/Air_Quality_Delhi/)

- Code available at: [https://github.com/adeel1997/Shiny-App-for-Air-Quality-in-Delhi](https://github.com/adeel1997/Shiny-App-for-Air-Quality-in-Delhi)


# Thank You